% CVPR 2025 Submission #1494. CONFIDENTIAL REVIEW COPY. DO NOT DISTRIBUTE.

\documentclass[10pt,twocolumn,letterpaper]{article}

%%%%%%%%% PAPER TYPE  - PLEASE UPDATE FOR FINAL VERSION
\usepackage[review]{cvpr}      % To produce the REVIEW version
% \usepackage{cvpr}              % To produce the CAMERA-READY version
% \usepackage[pagenumbers]{cvpr} % To force page numbers, e.g. for an arXiv version

% Include other packages here, before hyperref.
\usepackage{times}
\usepackage{epsfig}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{xcolor}
\usepackage{soul}
\usepackage{balance} % For balancing columns on last page

% It is strongly recommended to use hyperref, especially for the review version.
% hyperref with option pagebackref eases the reviewers' job.
% Please disable hyperref *only* if you encounter grave issues, e.g. with the
% file validation for the camera-ready version.
%
% If you comment hyperref and then uncomment it, you should delete
% ReviewTempalte.aux before re-running LaTeX.
% (Or just hit 'q' on the first LaTeX run, let it finish, and you
%  should be clear).
\usepackage[pagebackref,breaklinks,colorlinks]{hyperref}

% Support for easy cross-referencing
\usepackage[capitalize]{cleveref}
\crefname{section}{Sec.}{Secs.}
\Crefname{section}{Section}{Sections}
\Crefname{table}{Table}{Tables}
\crefname{table}{Tab.}{Tabs.}

% Define colors for different review aspects
\definecolor{strength}{RGB}{0,128,0}
\definecolor{weakness}{RGB}{178,34,34}
\definecolor{suggestion}{RGB}{0,0,139}

% Custom commands for review annotations
\newcommand{\strength}[1]{\textcolor{strength}{\textbf{[Strength] }#1}}
\newcommand{\weakness}[1]{\textcolor{weakness}{\textbf{[Weakness] }#1}}
\newcommand{\suggestion}[1]{\textcolor{suggestion}{\textbf{[Suggestion] }#1}}

%%%%%%%%% PAPER ID  - PLEASE UPDATE
\def\cvprPaperID{1494} % *** Enter the CVPR Paper ID here
\def\confName{CVPR}
\def\confYear{2025}

% Define paperID for compatibility
\def\paperID{\cvprPaperID}

%%%%%%%%% TITLE - PLEASE UPDATE
\title{Peer Review Report: Show and Segment: Universal Medical Image Segmentation via In-Context Learning}

%%%%%%%%% AUTHORS - TEAM MEMBERS WITH CONTACT INFORMATION
\author{Phaninder Reddy Masapeta (Team Lead)\\
Texas Tech University\\
Computer Science Department\\
{\tt\small Phaninder.Masapeta@ttu.edu}
\and
Sriya Dhakal\\
Texas Tech University\\
Computer Science Department\\
{\tt\small srdhakal@ttu.edu}
\and
Akhila Ravula\\
Texas Tech University\\
Computer Science Department\\
{\tt\small akravula@ttu.edu}
\and
Zezheng Zhang\\
Texas Tech University\\
Computer Science Department\\
{\tt\small zezzhang@ttu.edu}
\and
Scott Weeden\\
Texas Tech University\\
Computer Science Department\\
{\tt\small sweeden@ttu.edu}
}

\begin{document}

%%%%%%%%% TITLE
\maketitle

%%%%%%%%% ABSTRACT
\begin{abstract}
This document presents a comprehensive peer review of the paper "Show and Segment: Universal Medical Image Segmentation via In-Context Learning" submitted to CVPR 2025. Our five-member review team has evaluated the paper across multiple dimensions including technical contribution, experimental methodology, results validation, literature coverage, and presentation quality. We find that while the paper presents a novel and technically sound approach to medical image segmentation through in-context learning, there are several areas requiring clarification and improvement. Our consensus recommendation is Major Revision, contingent upon addressing the identified concerns regarding statistical validation, code availability, and performance analysis on challenging novel classes.
\end{abstract}

%%%%%%%%% BODY TEXT
%%%%%%%%% EXECUTIVE SUMMARY - ABSTRACT - TEAM LEAD
\input{sec/0_abstract}

%%%%%%%%% TECHNICAL CONTRIBUTION - TEAM MEMBER 1
\input{sec/1_technical_contribution}

%%%%%%%%% EXPERIMENTAL METHODOLOGY - TEAM MEMBER 2
\input{sec/2_experimental_methodology}

%%%%%%%%% RESULTS VALIDATION - TEAM MEMBER 3
\input{sec/3_results_validation}

%%%%%%%%% LITERATURE REVIEW - TEAM MEMBER 4
\input{sec/4_literature_review}

%%%%%%%%% PRESENTATION AND CLARITY - TEAM MEMBER 5
\input{sec/5_presentation_clarity}

%%%%%%%%% DETAILED TECHNICAL COMMENTS - ALL MEMBERS
\input{sec/6_detailed_comments}

%%%%%%%%% QUESTIONS FOR AUTHORS - ALL MEMBERS
\input{sec/7_questions_authors}

%%%%%%%%% MINOR ISSUES - TEAM MEMBER 5
\input{sec/8_minor_issues}

%%%%%%%%% META-REVIEW AND INTEGRATION - TEAM LEAD
\input{sec/9_meta_review}

% Balance columns on last page
\balance

%%%%%%%%% REFERENCES
{\small
\bibliographystyle{ieee_fullname}
\bibliography{main}
}

\end{document}
